Out-of-Sample Comparisons of Overfit Models

### 2014-03-28 paper.tex
Spellcheck paper

The condition~\ref{eq:27} requires that the acceptance region of
$\Lambda$ eventually contains any finite cylindar centered at the
origin. Again,~\eqref{eq:15} implies that statistics like the BIC
will always choose the smaller model for some DGPs, even when the
larger model will give more accurate forecasts. Both models may be
overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.

@@

In the picture, the true coefficients $\theta_2$ satisfy
\begin{equation*}
\theta_2'M_2'M_2\theta_2 > \var(\e_t)^{1/2} ((K_2 - K_1) / T)^{1/2}
\end{equation*}
so the center of the conditional distribution of $\bh{2T}$ given $\E_T
\oosB \leq 0$ is outside the acceptance region of the $F$-test. When
this is the case, the conditional probability that $\bh{2T}$ falls in
the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
uniformly distributed on the cylindar
\begin{equation*}
  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
  \theta_2'M_2' M_2 \theta_2 + d
\end{equation*}
for some positive $d$.

The AIC behaves essentially the same way. For the BIC, the radius of
the cylander centered at the origin increases with $T$ and eventually
encompasses the cylander centered at $M_2 \theta_2$, so it never
selects the alternative once $T$ is large enough.
\section{Monte Carlo}
\label{sec:mc}

This section presents two simulations that investigate the accuracy of
our theory in small samples.
We do several Monte Carlo exercises. The first looks at wheather our
theoretical results for the OOS average are accuarate: whether or not
the OOS average is approximately normal, and whether it is centered on
$\E_R \oosA$, $\E_T \oosB$, or somewhere else entierely. The second
issue is whether or not the \oost\ test is \emph{useful} for
conducting inference about $\E_T \oosB$. Our theoretical results
suggest that it may not be, because we require $P^2/T \to 0$ for
inference about $\E_T \oosB$ to be valid. A highly related issue is
whether other statistics are useful for conducting inference about
$\E_T \oosB$---again, our theoretical results suggest that they are
not.

We use the same DGP for all of these simulations, and it is described
in the next subsection. Results are presented in the subsection after
that. Simulations were conducted in R \citep{Rde:10} using the
\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
\emph{rlecuyer} \citep{SR:12} and graphs are produced using
\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
the fixed window, but recursive window results are available in a
separate Appendix and are broadly similary.

@@

To study the accuracy of our theoretical approximations, we first
estmate the coverage probabilities of OOS confidence intervals for
$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
construct the one-sided OOS interval defined in
Theorem~\ref{res:oostest}:
\begin{equation*}
  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
\end{equation*}
for $P = 10,\dots,2T/3$; we then calculate the percentage of
simulations where these intervals contain $\E_R \oosA$ and the
percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
of these quantities are easy to calculate (see
Section~\ref{sec:example}). For these calculations, we draw 2000
samples for each combination of the design parameters.

@@

Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
actual coverage is very close to the nominal coverage except when $P$
is very small.  The poor behavior for small $P$ is unsurprising, as it
simply means that the CLT is a poor approximation when the test sample
is small. The inteval for $T = 100$, $K = T/10$, and $c = 0$ is the
worst, with actual coverage near 85\% for most values of $P/T$. But
the others are much closer to nominal coverage, even for the
parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
the theoretical results to break down.

@@

We present the size simulations next, in
Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
We plot each OOS test's conditional rejection probability,
\begin{equation*}
  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
\end{equation*}
for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
$P$.  The $F$-test does not depend on $P$, so we calculate and
tabluate it's conditional rejection probability as a single value for
each combination of design parameters.

@@

Results using \citepos{Mcc:07} critical values are presented in
Figure~\ref{fig:mccracken} and are similar to those using Clark and
West's test.  For $c=0$ the rejection probability is nearly the test's
nominal size.  For $c=1$, the rejection probability increases with
$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
when $P/T = 2/3$.  Note that all of the simulations use the
parsimonious model.  McCracken's statistic overrejects here by
slightly less than Clark and West's, but still by a substantial
amount. Note that we are unable to plot results for McCracken's
statistic when $K/T = 10$, which is where the brakdown in Clark and
West's test is most pronounced.

@@

Since $M_2 \bh{2T}$ is normal, this conditional distribution is
invariant to reflection across the axes defined by the eigenvectors of
its covariance matrix. So when $\theta_2$ lies outside the cylindar
that contains the acceptance region of $\Lambda$, i.e. when
$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have%
\footnote{To keep the notation in these equations managable, define
  the information set $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2'
  V_T M_2 \theta_2 > c)$.} %
\begin{align*}
  \Pr[ \bh{2T}' M_2' V_T M_2 \bh{2T} \leq c \mid \Gs]
  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c \mid \Gs,~\bh{1T},~M_1 \bh{2T}] \mid \Gs \Big) \\
  & < 1/2
\end{align*}
since the inner conditional probability is less than 1/2.

@@

%  LocalWords:  ClM Mcc ClW MeR StW InK CCS CoS GiW GiR BRC HTF BoH
%  LocalWords:  Tib BaN AIC BoB AkA AkP Efr iR eq FPE th Dou iS iT dx
%  LocalWords:  JoD ixz Mcl RHS MSE homoskedastic Joh Widom TrW Sil
%  LocalWords:  BFP dy LLNs VeR rlecuyer RSQLite Sar tikzDevice TikZ
%  LocalWords:  PGF LaTeX jt test's CaT Coc BRW LeN RaW RaZ LeR ZeH
%  LocalWords:  lmtest Zei dbframe Hmsic Har xtable Dah booktabs FeE
%  LocalWords:  Bonferroni BWB Gia MeP indices Schwarz HaH Jong

>>>>

The condition~\ref{eq:27} requires that the acceptance region of
$\Lambda$ eventually contains any finite cylinder centered at the
origin. Again,~\eqref{eq:15} implies that statistics like the BIC
will always choose the smaller model for some DGPs, even when the
larger model will give more accurate forecasts. Both models may be
overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.

@@

In the picture, the true coefficients $\theta_2$ satisfy
\begin{equation*}
\theta_2'M_2'M_2\theta_2 > \var(\e_t)^{1/2} ((K_2 - K_1) / T)^{1/2}
\end{equation*}
so the center of the conditional distribution of $\bh{2T}$ given $\E_T
\oosB \leq 0$ is outside the acceptance region of the $F$-test. When
this is the case, the conditional probability that $\bh{2T}$ falls in
the rejection region is less than 1/2, since $M_2 \bh{2T}$ is
uniformly distributed on the cylinder
\begin{equation*}
  (M_2 \bh{2T} - M_2 \theta_2)'(M_2 \bh{2T} - M_2 \theta_2) =
  \theta_2'M_2' M_2 \theta_2 + d
\end{equation*}
for some positive $d$.

The AIC behaves essentially the same way. For the BIC, the radius of
the cylinder centered at the origin increases with $T$ and eventually
encompasses the cylinder centered at $M_2 \theta_2$, so it never
selects the alternative once $T$ is large enough.
\section{Monte Carlo}
\label{sec:mc}

This section presents two simulations that investigate the accuracy of
our theory in small samples.
We do several Monte Carlo exercises. The first looks at whether our
theoretical results for the OOS average are accurate: whether or not
the OOS average is approximately normal, and whether it is centered on
$\E_R \oosA$, $\E_T \oosB$, or somewhere else entirely. The second
issue is whether or not the \oost\ test is \emph{useful} for
conducting inference about $\E_T \oosB$. Our theoretical results
suggest that it may not be, because we require $P^2/T \to 0$ for
inference about $\E_T \oosB$ to be valid. A highly related issue is
whether other statistics are useful for conducting inference about
$\E_T \oosB$---again, our theoretical results suggest that they are
not.

We use the same DGP for all of these simulations, and it is described
in the next subsection. Results are presented in the subsection after
that. Simulations were conducted in R \citep{Rde:10} using the
\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
\emph{rlecuyer} \citep{SR:12} and graphs are produced using
\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
the fixed window, but recursive window results are available in a
separate Appendix and are broadly similar.

@@

To study the accuracy of our theoretical approximations, we first
estimate the coverage probabilities of OOS confidence intervals for
$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
construct the one-sided OOS interval defined in
Theorem~\ref{res:oostest}:
\begin{equation*}
  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
\end{equation*}
for $P = 10,\dots,2T/3$; we then calculate the percentage of
simulations where these intervals contain $\E_R \oosA$ and the
percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
of these quantities are easy to calculate (see
Section~\ref{sec:example}). For these calculations, we draw 2000
samples for each combination of the design parameters.

@@

Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
actual coverage is very close to the nominal coverage except when $P$
is very small.  The poor behavior for small $P$ is unsurprising, as it
simply means that the CLT is a poor approximation when the test sample
is small. The interval for $T = 100$, $K = T/10$, and $c = 0$ is the
worst, with actual coverage near 85\% for most values of $P/T$. But
the others are much closer to nominal coverage, even for the
parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
the theoretical results to break down.

@@

We present the size simulations next, in
Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
We plot each OOS test's conditional rejection probability,
\begin{equation*}
  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
\end{equation*}
for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
$P$.  The $F$-test does not depend on $P$, so we calculate and
tabulate it's conditional rejection probability as a single value for
each combination of design parameters.

@@

Results using \citepos{Mcc:07} critical values are presented in
Figure~\ref{fig:mccracken} and are similar to those using Clark and
West's test.  For $c=0$ the rejection probability is nearly the test's
nominal size.  For $c=1$, the rejection probability increases with
$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
when $P/T = 2/3$.  Note that all of the simulations use the
parsimonious model.  McCracken's statistic overrejects here by
slightly less than Clark and West's, but still by a substantial
amount. Note that we are unable to plot results for McCracken's
statistic when $K/T = 10$, which is where the breakdown in Clark and
West's test is most pronounced.

@@

Since $M_2 \bh{2T}$ is normal, this conditional distribution is
invariant to reflection across the axes defined by the eigenvectors of
its covariance matrix. So when $\theta_2$ lies outside the cylinder
that contains the acceptance region of $\Lambda$, i.e. when
$\theta_2'M_2' V_T M_2 \theta_2 > c$, we have%
\footnote{To keep the notation in these equations manageable, define
  the information set $\Gs = \sigma(\E_T \oosB \leq 0,~ \theta_2'M_2'
  V_T M_2 \theta_2 > c)$.} %
\begin{align*}
  \Pr[ \bh{2T}' M_2' V_T M_2 \bh{2T} \leq c \mid \Gs]
  &= \E\Big( \Pr[ \bh{2T}'M_2' V_T M_2 \bh{2T} \leq c \mid \Gs,~\bh{1T},~M_1 \bh{2T}] \mid \Gs \Big) \\
  & < 1/2
\end{align*}
since the inner conditional probability is less than 1/2.

@@

%  LocalWords:  ClM Mcc ClW MeR StW InK CCS CoS GiW GiR BRC HTF BoH '
%  LocalWords:  Tib BaN AIC BoB AkA AkP Efr iR eq FPE th Dou iS iT dx
%  LocalWords:  JoD ixz Mcl RHS MSE homoskedastic Joh Widom TrW Sil
%  LocalWords:  BFP dy LLNs VeR rlecuyer RSQLite Sar tikzDevice TikZ
%  LocalWords:  PGF LaTeX jt test's CaT Coc BRW LeN RaW RaZ LeR ZeH
%  LocalWords:  lmtest Zei dbframe Hmsic Har xtable Dah booktabs FeE
%  LocalWords:  Bonferroni BWB Gia MeP indices Schwarz HaH Jong i1 1R
%  LocalWords:  overcorrect 'X 's 2P i' 2i 2m 4C De eigenvectors 'M
%  LocalWords:  2'M 1'M
